---
title: "RNA species composition - treatments"
author:
  # - Jane Doe^[Institution Two, jane@example.org]      # add report authors (uncomment if using)
  # - John Doe^[Institution One, john@example.org]      # add a second report author (uncomment if using)
date: "Date: `r base::format(Sys.time(), '%d/%m/%Y')`"
always_allow_html: true
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: false
    self_contained: yes
    css: ../esr-styles.css
    highlight: pygments
    includes:
      after_body: ../esr_footer.html
  editor_options: 
    chunk_output_type: console
---

```{r setup, include=FALSE}
# setup default chunk settings
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE, fig.align = "center")
```

<img src="../images/ESR_logo.svg" style="position:absolute;top:19px;right:40px;width:23%;" />

## Info

General info:

- **The pie charts present only the RNA's from the datasets the user has chosen to analyse and RNA's that have been identified by the pipelines, rather than all the RNA's possibly present in the samples**
- *The total number of RNA counts are calculated for each RNA species, then the average of this is taken for each treatment group*
- *Values have been rounded*

```{r}
# load libraries
library(dplyr)
library(plotly)
library(gtools)
library(DT)

# for icons at bottom of doc
htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# read in pre-prepared count data
counts <- utils::read.csv("../prepare_counts/counts.csv")

# read in yaml config file
config <- yaml::yaml.load_file("../config/config.yaml")

# read in metadata
metadata <- utils::read.csv(base::file.path(config$metadata_path))

# subset all count data to the count data specified to be analysed by the user in the config file
# this will remove rows of data matching the said conditions

if(config$mirna_smrnaseq == "FALSE") {
  
  counts <- counts %>%
    dplyr::filter(!((rna_species == "mirna") & (pipeline == "smrnaseq")))
  
}

if(config$mirna_excerpt == "FALSE") {
  
  counts <- counts %>%
    dplyr::filter(!((rna_species == "mirna") & (pipeline == "excerpt")))
  
}

if(config$pirna_excerpt == "FALSE") {
  
  counts <- counts %>%
    dplyr::filter(!((rna_species == "pirna") & (pipeline == "excerpt")))
  
}

if(config$trna_excerpt == "FALSE") {
  
  counts <- counts %>%
    dplyr::filter(!((rna_species == "trna") & (pipeline == "excerpt")))
  
}

if(config$circrna_excerpt == "FALSE") {
  
  counts <- counts %>%
    dplyr::filter(!((rna_species == "circrna") & (pipeline == "excerpt")))
  
}

if(config$gencode_excerpt == "FALSE") {
  
  counts <- counts %>%
    dplyr::filter(!((rna_species == "gencode") & (pipeline == "excerpt")))
  
}

# create a vector to decide if the r chunks should be evaluated based on whether the dats from a given pipeline was analysed
smrnaseq_chunk_eval <- config$mirna_smrnaseq
excerpt_chunk_eval <- base::any("TRUE" %in% c(config$mirna_excerpt,
                                              config$pirna_excerpt,
                                              config$trna_excerpt,
                                              config$circrna_excerpt,
                                              config$gencode_excerpt))

# set up a colour list to colour RNA's by
colors_list <- base::list(
  "trna" = "#85C659",
  "mirna" = "#0097db",
  "pirna" = "#ec1515",
  "protein_coding" = "#febf2a",
  "Mt_rRNA" = "#784f96",
  "misc_RNA" = "#1abcc1",
  "retained_intron" = "#ffec8b",
  "processed_transcript" = "#88d4c3",
  "nonsense_mediated_decay" = "#1B9E77",
  "lincRNA" = "#ff9457",
  "antisense" = "#f190c1",
  "processed_pseudogene" = "#27408b",
  "snoRNA" = "#2b5540",
  "snRNA" = "#a91e69",
  "rRNA" = "#ff576e",
  "unprocessed_pseudogene" = "#27408b",
  "processed_transcript" = "#FAEBD7",
  "Mt_tRNA" = "#A52A2A",
  "TEC" = "#EE6A50",
  "transcribed_processed_pseudogene" = "#FFF8DC",
  "unitary_pseudogene" = "#8B8878",
  "polymorphic_pseudogene" = "#FF6A6A",
  "transcribed_unprocessed_pseudogene" = "#BA55D3",
  "macro_lncRNA" = "#FFE4E1",
  "non_coding" = "#8B7D7B",
  "sense_overlapping" = "#DB7093",
  "sense_intronic" = "#6C7B8B",
  "scaRNA" = "#FFFF00",
  "ribozyme" = "#EED2EE",
  "non_stop_decay" = "#00FF7F",
  "TR_J_gene" = "#FA8072"
)
```

Datasets analysed:

```{r, results = "asis"}
# print the datasets the user has chosen to analyse for this document
base::cat(base::paste0(" - mirna smrnaseq: ", config$mirna_smrnaseq, "\n",
                       " - mirna excerpt: ", config$mirna_excerpt, "\n",
                       " - pirna excerpt: ", config$pirna_excerpt, "\n",
                       " - trna excerpt: ", config$trna_excerpt, "\n",
                       " - circrna excerpt: ", config$circrna_excerpt, "\n",
                       " - gencode excerpt: ", config$gencode_excerpt, "\n"))
```

```{r, results = "asis"}
# print the number of samples analysed
base::cat(base::paste0("Total number of samples: ", length(unique(metadata$sample))))
```

Number of samples in each treatment group:

```{r, results = "asis"}
# print the number of samples in each treatment group
n_samples_by_treatment <- metadata %>%
  group_by(treatment) %>%
  dplyr::summarise(n_samples = n())

base::cat(base::paste0("- ", n_samples_by_treatment$treatment, ": ", n_samples_by_treatment$n_samples, "\n"))
```

## RNA species composition {.tabset .tabset-fade}

```{r}
# get the total RNA counts by RNA species, sample and pipeline (collapse individual RNAs)
data <- counts %>%
  dplyr::group_by(rna_species_2, sample, pipeline) %>%
  dplyr::summarise(total_raw_count = base::sum(raw_counts))

# join with metadata
data <- dplyr::left_join(data, metadata, by = "sample")

# get the average RNA counts by RNA species (and pipeline)
data <- data %>%
  dplyr::group_by(treatment, rna_species_2, pipeline) %>%
  dplyr::summarise(mean_total_raw_count = base::mean(total_raw_count)) %>%
  dplyr::arrange(dplyr::desc(treatment, mean_total_raw_count))

# create datatable of data
data %>%
  base::as.data.frame() %>%
  dplyr::mutate(across(c(treatment,
                         rna_species_2,
                         pipeline), base::as.factor)) %>%
  dplyr::mutate(across(c(mean_total_raw_count), base::as.integer)) %>%
  DT::datatable(selection = "single",
                filter = "top",
                rownames = FALSE,
                colnames = c("Treatment",
                             "RNA species",
                             "Pipeline",
                             "Average raw count"),
                extensions = base::list("ColReorder" = NULL,
                                        "Buttons" = NULL,
                                        "FixedColumns" = base::list(leftColumns=1)),
                options = list(
                  dom = "BRrltpi",
                  autoWidth = TRUE,
                  buttons =
                    list("copy",
                         list(extend = "collection",
                              buttons = c("csv", "excel", "pdf"),
                              text = "Download"),
                         I("colvis"))))
```

```{r, eval = smrnaseq_chunk_eval, results = 'asis'}
base::cat(base::paste0("### smrnaseq"))
```

```{r, eval = smrnaseq_chunk_eval, out.width = "100%"}
# filter to get only the data for the smrnaseq pipeline
data_smrnaseq <- data %>%
  dplyr::filter(pipeline == "smrnaseq")

# hard code the colours (for the high abundance RNA's because they're the most visible in these plots) so they
# are consistant between all the plots
data_smrnaseq$my_colour <- dplyr::recode(data_smrnaseq$rna_species_2, !!!colors_list)

# get maximum RNA count to scale bar plots to
max_range_barplot <- base::round(base::max(data_smrnaseq$mean_total_raw_count), digits = 0)

# make a list of the number of samples in each treatment group (so it can be passed to the tooltip below)
num_samples_by_treatment <- metadata %>%
  dplyr::group_by(treatment) %>%
  dplyr::summarise(num_samples = n())

# create a plot for each unique sample
# see issue I faced with a for loop in Rmd here: https://stackoverflow.com/questions/49990653/plotly-plot-doesnt-render-within-for-loop-of-rmarkdown-document
# and solution I applied here: https://github.com/ropensci/plotly/issues/273#issuecomment-195611009

htmltools::tagList(base::lapply(base::unique(gtools::mixedsort(data_smrnaseq$treatment)), function(x) { 
  
  # pie chart
  pie <- data_smrnaseq %>%
    dplyr::filter(treatment == x) %>%
    plotly::plot_ly(labels = ~rna_species_2,
                    values = ~mean_total_raw_count,
                    textposition = "inside",
                    textinfo = "label+percent",
                    insidetextfont = base::list(color = "#FFFFFF"),
                    hoverinfo = "text",
                    marker = base::list(colors = ~my_colour),
                    text = ~paste(" RNA species:", rna_species_2,
                                  "</br></br>",
                                  "Treatment:", treatment,
                                  "</br>",
                                  "Pipeline:", pipeline,
                                  "</br>",
                                  "Number of samples: ", (num_samples_by_treatment %>% dplyr::filter(treatment == x)) %>% dplyr::select(num_samples),
                                  "</br>",
                                  "Average raw count per sample: ", base::prettyNum(base::round(mean_total_raw_count, digits = 0), big.mark=","),
                                  "</br>",
                                  "Proportion of all RNA's identified: ", base::round((mean_total_raw_count/sum(mean_total_raw_count)*100), digits = 0), "%"),
                    showlegend = FALSE) %>%
    add_pie() %>%
    plotly::layout(title = x,
                   xaxis = base::list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE, domain = c(0.8,1)))
  
  # set plot size
  pie <- pie %>% layout(width = 200)
  
  # bar chart
  bar <- data_smrnaseq %>%
    dplyr::filter(treatment == x) %>%
    plotly::plot_ly(x = ~rna_species_2,
                    y = ~mean_total_raw_count,
                    type = "bar",
                    marker = base::list(color = ~my_colour),
                    hoverinfo = "text",
                    textposition = "none",
                    text = ~paste(" RNA species:", rna_species_2,
                                  "</br></br>",
                                  "Treatment:", treatment,
                                  "</br>",
                                  "Pipeline:", pipeline,
                                  "</br>",
                                  "Number of samples: ", (num_samples_by_treatment %>% dplyr::filter(treatment == x)) %>% dplyr::select(num_samples),
                                  "</br>",
                                  "Average raw count per sample: ", base::prettyNum(base::round(mean_total_raw_count, digits = 0), big.mark=","),
                                  "</br>",
                                  "Proportion of all RNA's identified: ", base::round((mean_total_raw_count/sum(mean_total_raw_count)*100), digits = 0), "%"),
                    showlegend = FALSE,
                    domain = base::list(x = c(0, 0.05))) %>%
    # get the same xaxis range for easy visual comparing between plots
    plotly::layout(yaxis = base::list(title = " ", range = c(0, max_range_barplot)),
                   xaxis = base::list(title = " ", showticklabels = FALSE))
  
  # set plot size
  bar <- bar %>% layout(width = 800)
  
  subplot(pie, bar, widths = c(0.8, 0.2))
  
}))
```

```{r, eval = excerpt_chunk_eval, results = 'asis'}
base::cat(base::paste0("### excerpt"))
```

```{r, eval = excerpt_chunk_eval, out.width = "100%"}
# filter to get only the data for the smrnaseq pipeline
data_excerpt <- data %>%
  dplyr::filter(pipeline == "excerpt")

# hard code the colours (for the high abundance RNA's because they're the most visible in these plots) so they
# are consistant between all the plots
data_excerpt$my_colour <- dplyr::recode(data_excerpt$rna_species_2, !!!colors_list)

# get maximum RNA count to scale bar plots to
max_range_barplot <- base::round(base::max(data_excerpt$mean_total_raw_count), digits = 0)

# make a list of the number of samples in each treatment group (so it can be passed to the tooltip below)
num_samples_by_treatment <- metadata %>%
  dplyr::group_by(treatment) %>%
  dplyr::summarise(num_samples = n())

# create a plot for each unique sample
# see issue I faced with a for loop in Rmd here: https://stackoverflow.com/questions/49990653/plotly-plot-doesnt-render-within-for-loop-of-rmarkdown-document
# and solution I applied here: https://github.com/ropensci/plotly/issues/273#issuecomment-195611009

htmltools::tagList(base::lapply(base::unique(gtools::mixedsort(data_excerpt$treatment)), function(x) { 
  
  # pie chart
  pie <- data_excerpt %>%
    dplyr::filter(treatment == x) %>%
    plotly::plot_ly(labels = ~rna_species_2,
                    values = ~mean_total_raw_count,
                    textposition = "inside",
                    textinfo = "label+percent",
                    insidetextfont = base::list(color = "#FFFFFF"),
                    hoverinfo = "text",
                    marker = base::list(colors = ~my_colour),
                    text = ~paste(" RNA species:", rna_species_2,
                                  "</br></br>",
                                  "Treatment:", treatment,
                                  "</br>",
                                  "Pipeline:", pipeline,
                                  "</br>",
                                  "Number of samples: ", (num_samples_by_treatment %>% dplyr::filter(treatment == x)) %>% dplyr::select(num_samples),
                                  "</br>",
                                  "Average raw count per sample: ", base::prettyNum(base::round(mean_total_raw_count, digits = 0), big.mark=","),
                                  "</br>",
                                  "Proportion of all RNA's identified: ", base::round((mean_total_raw_count/sum(mean_total_raw_count)*100), digits = 0), "%"),
                    showlegend = FALSE) %>%
    add_pie() %>%
    plotly::layout(title = x,
                   xaxis = base::list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE, domain = c(0.8,1)))
  
  # set plot size
  pie <- pie %>% layout(width = 200)
  
  # bar chart
  bar <- data_excerpt %>%
    dplyr::filter(treatment == x) %>%
    plotly::plot_ly(x = ~rna_species_2,
                    y = ~mean_total_raw_count,
                    type = "bar",
                    marker = base::list(color = ~my_colour),
                    hoverinfo = "text",
                    textposition = "none",
                    text = ~paste(" RNA species:", rna_species_2,
                                  "</br></br>",
                                  "Treatment:", treatment,
                                  "</br>",
                                  "Pipeline:", pipeline,
                                  "</br>",
                                  "Number of samples: ", (num_samples_by_treatment %>% dplyr::filter(treatment == x)) %>% dplyr::select(num_samples),
                                  "</br>",
                                  "Average raw count per sample: ", base::prettyNum(base::round(mean_total_raw_count, digits = 0), big.mark=","),
                                  "</br>",
                                  "Proportion of all RNA's identified: ", base::round((mean_total_raw_count/sum(mean_total_raw_count)*100), digits = 0), "%"),
                    showlegend = FALSE,
                    domain = base::list(x = c(0, 0.05))) %>%
    # get the same xaxis range for easy visual comparing between plots
    plotly::layout(yaxis = base::list(title = " ", range = c(0, max_range_barplot)),
                   xaxis = base::list(title = " ", showticklabels = FALSE))
  
  # set plot size
  bar <- bar %>% layout(width = 800)
  
  subplot(pie, bar, widths = c(0.8, 0.2))
  
}))
```

```{r, cleanup, results = "hide"}
# clean up
rm(list = ls())
```
