---
title: "Presence/absence analysis"
author:
  # - Jane Doe^[Institution Two, jane@example.org]      # add report authors (uncomment if using)
  # - John Doe^[Institution One, john@example.org]      # add a second report author (uncomment if using)
date: "Date: `r base::format(Sys.time(), '%d/%m/%Y')`"
output:
  html_document:
    code_download: true
    toc: false
  editor_options: 
    chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE, fig.align = "center")
```

## Info

```{r}
# load libraries
library(dplyr)
library(plotly)
library(gtools)
library(DT)

# read in pre-prepared count data
counts <- utils::read.csv("../prepare_counts/counts.csv")

# read in yaml config file
config <- yaml::yaml.load_file("../config/config.yaml")

# read in metadata
metadata <- utils::read.csv(file.path(config$metadata))

# make a little true/false vector that defines whether or not to evaluate rmarkdown chunks based on the number of treatments in the metadata file (up to 6 treatments)
treatments_eval <- rep(TRUE, length(unique(metadata$treatment)))
treatments_eval <- append(treatments_eval, rep(FALSE, 6))
treatments_eval <- treatments_eval[1:6]

# create a function for plotting datatables with my parameters
create_dt <- function(data) {
  data %>%
    dplyr::mutate(across(c(rna_species), base::as.factor)) %>%
    DT::datatable(filter = "top",
                  rownames = FALSE,
                  colnames = c("RNA", "RNA species"),
                  extensions = list("ColReorder" = NULL,
                                    "Buttons" = NULL,
                                    "FixedColumns" = list(leftColumns=1)),
                  options = list(
                    dom = "BRrltpi",
                    autoWidth = TRUE,
                    buttons =
                      list("copy",
                           list(extend = "collection",
                                buttons = c("csv", "excel", "pdf"),
                                text = "Download"),
                           I("colvis"))))
}
```

Datasets analysed:

```{r, results = "asis"}
# print the datasets the user has chosen to analyse for this document
base::cat(base::paste0(" - mirna smrnaseq: ", config$mirna_smrnaseq, "\n",
                       " - mirna excerpt: ", config$mirna_excerpt, "\n",
                       " - pirna excerpt: ", config$pirna_excerpt, "\n",
                       " - trna excerpt: ", config$trna_excerpt, "\n",
                       " - circrna excerpt: ", config$circrna_excerpt, "\n",
                       " - gencode excerpt: ", config$gencode_excerpt, "\n"))
```

```{r, results = "asis"}
# print the number of samples analysed
base::cat(base::paste0("Total number of samples: ", length(unique(metadata$sample))))
```

Number of samples in each treatment group:

```{r, results = "asis"}
# print the number of samples in each treatment group
n_samples_by_treatment <- metadata %>%
  group_by(treatment) %>%
  dplyr::summarise(n_samples = n())

base::cat(base::paste0("- ", n_samples_by_treatment$treatment, ": ", n_samples_by_treatment$n_samples, "\n"))
```

# {.tabset .tabset-fade}

## smrnaseq

```{r}
# filter so looking at the data from one pipeline (excerpt)
counts_smrnaseq <- counts %>%
  dplyr::filter(pipeline == "smrnaseq")

# join counts with metadata
counts_smrnaseq_w_meta <- dplyr::full_join(counts_smrnaseq, metadata, by = "sample")

# separate the dataset by each treatment group
data_list <- counts_smrnaseq_w_meta %>%
  dplyr::group_split(treatment, .keep = TRUE)

# format and get only the columns we're interested in
data_list <- base::lapply(data_list, function(x)
  x %>%
    base::as.data.frame() %>%
    select(rna, sample, raw_counts, treatment)
)

# get number of samples
num_samples <- length(unique(metadata$sample))

# create a dataframe pairing all the rnas with their RNA species
rna_species_pairs <- counts %>%
  select(rna, rna_species) %>%
  dplyr::distinct(rna, .keep_all = TRUE)

# get the rna's that are present in ALL samples (for each treatment group)
rnas_in_all_samples <- base::lapply(data_list, function(x)
 
    x %>%
      # filter out samples that had a count of zero (the rna WASN'T present in that sample)
      dplyr::filter(raw_counts != 0) %>%
      dplyr::group_by(rna) %>%
      dplyr::summarise(num_samples_present_in = n()) %>%
      # then get the rna's that were present in all samples (num_samples_present_in is the same as the number of sample's in that treatment group)
      dplyr::filter(num_samples_present_in == num_samples) %>%
      # add back rna species column
      dplyr::left_join(rna_species_pairs, by = "rna")

)

# get the rna's that are present in the MAJORITY (75%) of samples (for each treatment group)
rnas_in_majority_samples <- base::lapply(data_list, function(x)
 
    x %>%
      # filter out samples that had a count of zero (the rna WASN'T present in that sample)
      dplyr::filter(raw_counts != 0) %>%
      dplyr::group_by(rna) %>%
      dplyr::summarise(num_samples_present_in = n()) %>%
      # then get the rna's that were present in the majority of samples
      dplyr::filter(num_samples_present_in >= num_samples * 0.75) %>%
      # add back rna species column
      dplyr::left_join(rna_species_pairs, by = "rna")

)

# get the rna's that are present in SEVERAL OR MORE (25% or more) of samples (for each treatment group)
rnas_in_several_samples <- base::lapply(data_list, function(x)
 
    x %>%
      # filter out samples that had a count of zero (the rna WASN'T present in that sample)
      dplyr::filter(raw_counts != 0) %>%
      dplyr::group_by(rna) %>%
      dplyr::summarise(num_samples_present_in = n()) %>%
      # then get the rna's that were present in several samples
      dplyr::filter(num_samples_present_in >= num_samples * 0.25) %>%
      # add back rna species column
      dplyr::left_join(rna_species_pairs, by = "rna")

)

# get the rna's that are present in AT LEAST ONE sample (for each treatment group)
rnas_in_at_least_one_sample <- base::lapply(data_list, function(x)
 
    x %>%
      # filter out samples that had a count of zero (the rna WASN'T present in that sample)
      dplyr::filter(raw_counts != 0) %>%
      dplyr::group_by(rna) %>%
      dplyr::summarise(num_samples_present_in = n()) %>%
      # then get the rna's that were present in at least one sample (num_samples_present_in is at least one)
      dplyr::filter(num_samples_present_in >= 1) %>%
      # add back rna species column
      dplyr::left_join(rna_species_pairs, by = "rna")

)
```

### RNA's present in EVERY sample in one treatment group that was NOT found in AT LEAST ONE sample in another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

### RNA's present in the MAJORITY (75% or more) of samples in one treatment group but NOT in the MAJORITY (75% or more) of samples in another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

### RNA's present in the MAJORITY (75% or more) of samples in one treatment group but NOT in SEVERAL (25% or more) samples in another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

### RNA’s present in SEVERAL (25% or more) samples in one treatment group but NOT in SEVERAL (25% or more) samples in another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

### RNA's present in AT LEAST ONE sample of one treatment group but NOT present in AT LEAST ONE sample of another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

## excerpt

```{r}
# filter so looking at the data from one pipeline (excerpt)
counts_excerpt <- counts %>%
  dplyr::filter(pipeline == "excerpt")

# join counts with metadata
counts_excerpt_w_meta <- dplyr::full_join(counts_excerpt, metadata, by = "sample")

# separate the dataset by each treatment group
data_list <- counts_excerpt_w_meta %>%
  dplyr::group_split(treatment, .keep = TRUE)

# format and get only the columns we're interested in
data_list <- base::lapply(data_list, function(x)
  x %>%
    base::as.data.frame() %>%
    select(rna, sample, raw_counts, treatment)
)

# get number of samples
num_samples <- length(unique(metadata$sample))

# create a dataframe pairing all the rnas with their RNA species
rna_species_pairs <- counts %>%
  select(rna, rna_species) %>%
  dplyr::distinct(rna, .keep_all = TRUE)

# get the rna's that are present in ALL samples (for each treatment group)
rnas_in_all_samples <- base::lapply(data_list, function(x)
 
    x %>%
      # filter out samples that had a count of zero (the rna WASN'T present in that sample)
      dplyr::filter(raw_counts != 0) %>%
      dplyr::group_by(rna) %>%
      dplyr::summarise(num_samples_present_in = n()) %>%
      # then get the rna's that were present in all samples (num_samples_present_in is the same as the number of sample's in that treatment group)
      dplyr::filter(num_samples_present_in == num_samples) %>%
      # add back rna species column
      dplyr::left_join(rna_species_pairs, by = "rna")

)

# get the rna's that are present in the MAJORITY (75%) of samples (for each treatment group)
rnas_in_majority_samples <- base::lapply(data_list, function(x)
 
    x %>%
      # filter out samples that had a count of zero (the rna WASN'T present in that sample)
      dplyr::filter(raw_counts != 0) %>%
      dplyr::group_by(rna) %>%
      dplyr::summarise(num_samples_present_in = n()) %>%
      # then get the rna's that were present in the majority of samples
      dplyr::filter(num_samples_present_in >= num_samples * 0.75) %>%
      # add back rna species column
      dplyr::left_join(rna_species_pairs, by = "rna")

)

# get the rna's that are present in SEVERAL OR MORE (25% or more) of samples (for each treatment group)
rnas_in_several_samples <- base::lapply(data_list, function(x)
 
    x %>%
      # filter out samples that had a count of zero (the rna WASN'T present in that sample)
      dplyr::filter(raw_counts != 0) %>%
      dplyr::group_by(rna) %>%
      dplyr::summarise(num_samples_present_in = n()) %>%
      # then get the rna's that were present in several samples
      dplyr::filter(num_samples_present_in >= num_samples * 0.25) %>%
      # add back rna species column
      dplyr::left_join(rna_species_pairs, by = "rna")

)

# get the rna's that are present in AT LEAST ONE sample (for each treatment group)
rnas_in_at_least_one_sample <- base::lapply(data_list, function(x)
 
    x %>%
      # filter out samples that had a count of zero (the rna WASN'T present in that sample)
      dplyr::filter(raw_counts != 0) %>%
      dplyr::group_by(rna) %>%
      dplyr::summarise(num_samples_present_in = n()) %>%
      # then get the rna's that were present in at least one sample (num_samples_present_in is at least one)
      dplyr::filter(num_samples_present_in >= 1) %>%
      # add back rna species column
      dplyr::left_join(rna_species_pairs, by = "rna")

)
```

### RNA's present in EVERY sample in one treatment group that was NOT found in AT LEAST ONE sample in another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[1]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_all_samples[[6]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_all_samples[[5]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_all_samples[[4]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_all_samples[[3]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_all_samples[[2]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

### RNA's present in the MAJORITY (75% or more) of samples in one treatment group but NOT in the MAJORITY (75% or more) of samples in another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_majority_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_majority_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_majority_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_majority_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_majority_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

### RNA's present in the MAJORITY (75% or more) of samples in one treatment group but NOT in SEVERAL (25% or more) samples in another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[1]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_majority_samples[[6]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_majority_samples[[5]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_majority_samples[[4]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_majority_samples[[3]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_majority_samples[[2]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

### RNA’s present in SEVERAL (25% or more) samples in one treatment group but NOT in SEVERAL (25% or more) samples in another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[1]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_several_samples[[6]], rnas_in_several_samples[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_several_samples[[5]], rnas_in_several_samples[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_several_samples[[4]], rnas_in_several_samples[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_several_samples[[3]], rnas_in_several_samples[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_several_samples[[2]], rnas_in_several_samples[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

### RNA's present in AT LEAST ONE sample of one treatment group but NOT present in AT LEAST ONE sample of another treatment group {.tabset .tabset-fade}

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[1]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[1]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[6]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[6]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[6], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[6]] %>% dplyr::distinct(treatment), " vs. ", data_list[[5]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[6]}
anti_join(rnas_in_at_least_one_sample[[6]], rnas_in_at_least_one_sample[[5]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[5], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[5]] %>% dplyr::distinct(treatment), " vs. ", data_list[[4]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[5]}
anti_join(rnas_in_at_least_one_sample[[5]], rnas_in_at_least_one_sample[[4]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[4], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[4]] %>% dplyr::distinct(treatment), " vs. ", data_list[[3]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[4]}
anti_join(rnas_in_at_least_one_sample[[4]], rnas_in_at_least_one_sample[[3]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[3], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[3]] %>% dplyr::distinct(treatment), " vs. ", data_list[[2]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[3]}
anti_join(rnas_in_at_least_one_sample[[3]], rnas_in_at_least_one_sample[[2]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, eval = treatments_eval[2], results = "asis"}
# print the treatment group comparisons the user has chosen to analyse
base::cat(base::paste0("#### ", data_list[[2]] %>% dplyr::distinct(treatment), " vs. ", data_list[[1]] %>% dplyr::distinct(treatment)))
```

```{r, eval = treatments_eval[2]}
anti_join(rnas_in_at_least_one_sample[[2]], rnas_in_at_least_one_sample[[1]], by = "rna") %>%
  dplyr::select(rna, rna_species) %>%
  create_dt()
```

```{r, cleanup, results = "hide"}
# clean up
rm(list = ls())
```
